\Large \bf Vigor: Toward Carrier-Grade Software Network Functions

### 2016-10-29 doc/paper/paper.tex
Rephrased the validation criteria.

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[]{algorithm2e}
\usepackage{changepage}
\usepackage{hyperref}
\definecolor{mygreen}{rgb}{0.1,0.5,0.1}
\definecolor{myblue}{rgb}{0.1,0.1,0.7}

@@

When symbolically executing a code path, the SEE checks whether any asserts fail.

@@

To validate a model behavior under certain circumstances means to ensure the
behavior agrees with the specification, or is more relaxed (i.e., admits more
behaviors than the spec). Suppose that, for the input \(I\) to the prefix of an
execution trace (a ``run''), the specification produces the output $O_s$, and
the model produces the case output \(O_m\). Then the model is valid iff for all
call sequences performed during the exhaustive SE, \(O_m\) contains \(O_s\).

More formally:
\begin{enumerate}
\item \(C\): A call sequence, or a run (\(C=Ci+Co\)) consists of a run input and
  run output. It summarizes a particular interaction scenario with the model. It
  consists of the calls to component API functions (with function names,
  arguments and return values), and leaves out all other details like other
  calls or unrelated path conditions.
\item \(Ci\): The run input (\(Ci = <Fi,Fo>i=0..n-1 + Fin\)) is a set of:
  function names, function inputs(\(Fi\)) for all the functions in the sequence
  and function outputs(\(Fo\)) for all but the last call.
\item \(Co\): The run output (\(Co = Fon\)) is the output of the last API
  function call in the sequence.
\item \(Fi\): The function input (\(Fi = fun\_name + args +
  arg\_pointee\_vals\_before + constraints\)) consists of the function arguments
  (possibly symbolic), and constraints bounding these arguments (specifically,
  the transitive closure of all the constraints involving the symbols mentioned
  in the formulas for the arguments). For a pointer argument (which must point
  to a concrete address --- practical limitation), the pointee must be
  considered according to the \S\ref{sec:handling-pointers}. We use the
  numerical value of the pointer to detect aliasing between the variables, and
  then throw it away, since we forbid pointer comparison anyway.
\item \(Fo\): The function output (\(Fo = ret\_val + pointee\_vals\_after +
  constraints\)) is its return value and the pointee values for the output
  pointer arguments, as well as the constraints for all the symbols involved
  (transitive closure, same as above).
\end{enumerate}

Let us represent the formal specification and the symbolic model total states by
large sets. A total state consists of variables V, bound by logical formulas F.
So, the specification and model total states are:
\[
\{V_s : F_s(V_s)\} and \{V_m : F_m(V_m)\}
\]
The output is then simply a projection of the corresponding state. The
projection (P) gives the output variables (return value and output pointers of
the tip call):
\[
OV_s = P_s(V_s): OV_m = P_m(V_m).
\]

@@

With the introduced definitions, the following formulas define the outputs:
\[
O_s = \{P_s(V_s): \forall V_s F_s(V_s)\} \\
O_m = \{P_m(V_m) : \forall V_m F_m(V_m)\}
\]
Then, the model exhibits all the specified behaviours (and may be some more) iff
\(O_s \in O_m\), or:
\[
\forall V_s : F_s(V_s) \exists V_m : F_m (V_m) \cap P_s(V_s) = P_m(V_m)
\]
This formula in general is too difficult for the existing SMT solvers because of
the quantifier. However, due to similarities in the model and the specification
it is easy to find appropriate values for \(V_m\) --- they happen to be some
values from Vs. Let us call this assignment \(A\). \(A\) by construction
satisfies the equality \(P_s(V_s)=P_m(A(V_s))\). So the condition becomes:
\[
\forall V_s : F_s(V_s) \rightarrow F_m(A(V_s))
\]
--- a typical validity query, which we pass  to an SMT solver.

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[]{algorithm2e}
\usepackage{changepage}
\usepackage{hyperref}
\definecolor{mygreen}{rgb}{0.1,0.5,0.1}
\definecolor{myblue}{rgb}{0.1,0.1,0.7}

@@

When symbolically executing a code path, the SEE checks whether any assert fail.

@@

To validate a model behavior under certain circumstances means to ensure the
behavior agrees with the specification, or is more relaxed (i.e., admits more
behaviors than the spec). Suppose that, for the input \(I\) to the prefix of an
execution trace (a ``run''), the specification produces the output $O_s$, and
the model produces the output \(O_m\). Then the model is valid iff for all call
sequences performed during the exhaustive SE, \(O_m\) contains \(O_s\).

More formally:
\begin{enumerate}
\item \(F^i\): The function input (\(F^i = fun\_name + args +
  arg\_pointee\_vals\_before + constraints\)) consists of the function arguments
  (possibly symbolic), and constraints bounding these arguments (specifically,
  the transitive closure of all the constraints involving the symbols mentioned
  in the formulas for the arguments). For a pointer argument (which must point
  to a concrete address --- a practical limitation), the pointee must be
  considered according to the \S\ref{sec:handling-pointers}. We use the
  numerical value of the pointer to detect aliasing between the variables, and
  then throw it away, since we forbid pointer comparison anyway.
\item \(F^o\): The function output (\(F^o = ret\_val + pointee\_vals\_after +
  constraints\)) is its return value and the pointee values for the output
  pointer arguments, as well as the constraints for all the symbols involved
  (transitive closure, same as for \(F^i\)).
\item \(I\): The run input (\(I = <F^i,F^o>_{i=0..n-1} + F^i_n\)) is a set of:
  function names, function inputs(\(F^i\)) for all the functions in the sequence
  and function outputs(\(F^o\)) for all but the last call.
\item \(O\): The run output (\(O = F^o_n\)) is the output of the last API
  function call in the sequence.
\item \(C\): A call sequence(= run), (\(C=I+O\)) consists of a run input and
  run output. It summarizes a particular interaction scenario with the model. It
  consists of the calls to component API functions (with function names,
  arguments and return values), and leaves out all other details like other
  calls or unrelated path conditions.
\end{enumerate}

Let us represent the formal specification and the symbolic model total states by
large sets. A total state consists of variables V, bound by logical formulas F.
So, the specification and model total states are:
\[
  \begin{aligned}
  &\mathrm{total~specification~state} = \{V_s : F_s(V_s)\}\\
  &\mathrm{total~model~state} = \{V_m : F_m(V_m)\}
  \end{aligned}
\]
The output is then simply a projection of the corresponding state. The
projection (\(P\)) gives the output variables (return value and output pointers of
the tip call):
\[
OV_s = P_s(V_s): OV_m = P_m(V_m).
\]

@@

With the introduced definitions, the following formulas define the outputs:
\[
  \begin{aligned}
    &O_s = \{P_s(V_s): \forall V_s F_s(V_s)\} \\
    &O_m = \{P_m(V_m) : \forall V_m F_m(V_m)\}
  \end{aligned}
\]
Then, the model exhibits all the specified behaviours (and may be some more) iff
\(O_s \in O_m\), or:
\[
\forall V_s : F_s(V_s) \exists V_m : F_m (V_m) \cap P_s(V_s) = P_m(V_m)
\]
This formula in general is too difficult for the existing SMT solvers because of
the quantifier. However, due to similarities in the model and the specification
it is easy to find appropriate values for \(V_m\) --- they happen to be some
values from \(Vs\). Let us call this assignment \(A\). \(A\) by construction
satisfies the equality \(P_s(V_s)=P_m(A(V_s))\). So the condition becomes:
\[
\forall V_s : F_s(V_s) \rightarrow F_m(A(V_s))
\]
--- which we formulate as an assertion and let the formal verification engine
decide its validity.
